### 2021-04-20 submissions/CPC_response_to_reviewers.md

	**The make_examples.sh file has been removed.**

3. It appears that there are no tests associated with the library. This is a bit surprising - I would expect regression test coverage on the basic API functionality.

**TO DO: consult Josh about appropriate tests for RadLib**

5. CMake build system:
    1.	Consider installing a “RadLib.cmake” file for downstream usage by CMake-based projects. This helps downstream build systems configure for RadLib usage (setting include paths, etc.).

		**Installation now includes a radlib.cmake file, located in the installed/cmake/radlib directory, for downstream usage.**

    3.	probably shouldn’t specify optimize or debug flags directly, as CMake will provide appropriate values on most platforms.

@@

		**Build has been updated to reflect this.**

    3.	the default build type isn’t defaulting to Release for me; it remains blank.

		**The authors have not experienced problems with this, but have verified that it works correctly. Note that the build type can be overridden by IDE build settings, among other things, and that this may be a system issue specific to the reviewer.**

    5.	I suggest not using verbose makefiles by default.

  		**Build has be updated so that verbose makefiles are no longer the default.**

    3.	Using GLOB to install the headers is not the appropriate CMake approach.

		**Build updated accordingly; GLOB no longer used to install header files.**

    5.	the data files are not copied into the examples build directory, meaning that the example executables do not run.

		**The authors have experienced no issues running the example executables from either the build/examples directory or directly from the examples directory.**

    7.	The run-examples.sh script is not helpful as it is not installed into the build directory where the executables are produced and doesn’t have path information to actually run the executables.

@@

Considering all these, I think that this CPiP submission is definitely within the scope of the journal and of interest to the research community. However, the following concerns must be addressed before the submission is considered for publication.

**The authors would like to thank the reviewer for their insightful comments and suggestions. As members of the combustion community, we heartily agree that a tool like RadLib could benefit researchers and facilitate radiation model development for combustion CFD.**

1) I could not successfully build and run the library in two different Linux systems. In both cases, first, the cmake returned an error:
"CMake Error at c++/CMakeLists.txt:34 (install): install TARGETS given no ARCHIVE DESTINATION for static library target "radlib"."
I could resolve this by adding ARCHIVE DESTINATION line on the c++/CMakeLists.txt file.
But, then on during "make" my installation was interrupted several times because of missing packages in my Python installation.
I would strongly recommend that the authors modify the installation instructions to include: a) list of dependencies (i.e., what compilers, what versions of python, what python packages, etc.), b) how to install the dependencies before building RadLib, c) a way to build RadLib with either only C++ or only Python. These installation notes do not necessarily need to be in the main manuscript, but they must be in the installation README of the code package.

	**The CMake build system has been updated such that ARCHIVE DESTINATION is explicitly specified, so that error should no longer occur. A build option has been added that makes the Python interface installation optional. Note that the C++ source code is required to install the Python interface, so there is no option to build only the Python interface. All of this information has been added to the ```README.md``` files located in the root directory and the ```build``` directory along with a more thorough list of software dependencies and required Python packages.**

### 2021-04-20 submissions/CPC_response_to_reviewers.md

3. It appears that there are no tests associated with the library. This is a bit surprising - I would expect regression test coverage on the basic API functionality.

**TO DO: consult Josh about appropriate tests for RadLib**

5. CMake build system:
    1.	Consider installing a “RadLib.cmake” file for downstream usage by CMake-based projects. This helps downstream build systems configure for RadLib usage (setting include paths, etc.).

		**Installation now includes a ```radlib.cmake``` file, located in the ```installed/cmake/radlib``` directory, for downstream usage.**

@@

    3.	Using GLOB to install the headers is not the appropriate CMake approach.

		**Build updated accordingly; GLOB no longer used to install header files.**

    5.	the data files are not copied into the examples build directory, meaning that the example executables do not run.

		**The authors have experienced no issues running the example executables from either the ```build/examples``` directory or directly from the ```examples``` directory.**

@@

    7.	The run-examples.sh script is not helpful as it is not installed into the build directory where the executables are produced and doesn’t have path information to actually run the executables.

		**Executables are built within the example folders in addition to the build directories, so ```run_examples.sh``` runs without any issues and serves as a simple illustration of the example cases.**

@@

Considering all these, I think that this CPiP submission is definitely within the scope of the journal and of interest to the research community. However, the following concerns must be addressed before the submission is considered for publication.

**The authors would like to thank the reviewer for their insightful comments and suggestions. As members of the combustion community, we heartily agree that a tool like RadLib could benefit researchers and facilitate radiation model development for combustion CFD.**

1) I could not successfully build and run the library in two different Linux systems. In both cases, first, the cmake returned an error:
"CMake Error at c++/CMakeLists.txt:34 (install): install TARGETS given no ARCHIVE DESTINATION for static library target "radlib"."
I could resolve this by adding ARCHIVE DESTINATION line on the c++/CMakeLists.txt file.
But, then on during "make" my installation was interrupted several times because of missing packages in my Python installation.
I would strongly recommend that the authors modify the installation instructions to include: a) list of dependencies (i.e., what compilers, what versions of python, what python packages, etc.), b) how to install the dependencies before building RadLib, c) a way to build RadLib with either only C++ or only Python. These installation notes do not necessarily need to be in the main manuscript, but they must be in the installation README of the code package.

	**The CMake build system has been updated such that ```ARCHIVE DESTINATION``` is explicitly specified, so that error should no longer occur. A build option has been added that makes the Python interface installation optional. Note that the C++ source code is required to install the Python interface, so there is no option to build only the Python interface. All of this information has been added to the ```README.md``` files located in the root directory and the ```build``` directory along with a more thorough list of software dependencies and required Python packages.**
